Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-01 Paper.tex
Fixed error with a space between \usepackage [autostyle]{csquotes}.
Fixed warnings for reference doesn't exist.
Trying to fix an error in build on l. 2111.
Trying to get build to pass.

\documentclass[9pt,oneside]{amsart}
\usepackage{cancel}
%\usepackage{tweaklist}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{underscore}
%\usepackage{lipsum} % to generate filler text for testing of document rendering
\usepackage[english]{babel}
\usepackage [autostyle]{csquotes}
\MakeOuterQuote{"}
\usepackage[bookmarks=true, unicode=true, pdftitle={Ethereum Yellow Paper: a formal specification of Ethereum, a programmable blockchain}, pdfauthor={Gavin Wood and others as per https://github.com/ethereum/yellowpaper/commits/master},pdfkeywords={Ethereum, Yellow Paper, blockchain, virtual machine, cryptography, decentralised, singleton, transaction, generalised},pdfborder={0 0 0.5 [1 3]}]{hyperref}
%,pagebackref=true

@@

% Tabu seems more flexible, and generally better.
\usepackage{tabu}

@@

\usepackage[utf8]{inputenc}

@@

$G_{\mathrm{memory}}$ & 3 & This is paid for every additional word when expanding memory. \hypertarget{txcreate}{\\

@@

\begin{tabularx}{\textwidth}{rlrrX}
\midrule
0xf4 & {\small DELEGATECALL} & 6 & 1 & Message-call into this account with an alternative account's code, but persisting the current values for {\it sender} and {\it value}. Compared with {\small CALL}, {\small DELEGATECALL} takes one fewer arguments.  The omitted argument is $\boldsymbol{\mu}_\mathbf{s}[2]$. As a result, $\boldsymbol{\mu}_\mathbf{s}[3]$, $\boldsymbol{\mu}_\mathbf{s}[4]$, $\boldsymbol{\mu}_\mathbf{s}[5]$ and $\boldsymbol{\mu}_\mathbf{s}[6]$ in the definition of {\small CALL} should respectively be replaced with $\boldsymbol{\mu}_\mathbf{s}[2]$, $\boldsymbol{\mu}_\mathbf{s}[3]$, $\boldsymbol{\mu}_\mathbf{s}[4]$ and $\boldsymbol{\mu}_\mathbf{s}[5]$. Otherwise it is exactly equivalent to {\small CALL} except: \\
&&&& $(\boldsymbol{\sigma}', g', A^+, \mathbf{o}) \equiv \begin{cases}\begin{array}{l}\Theta(\boldsymbol{\sigma}^*, I_\mathbf{s}, I_\mathbf{o}, I_\mathbf{a}, t,\\\quad \boldsymbol{\mu}_\mathbf{s}[0], I_\mathbf{p}, 0, \hyperlink{I v}{I_\mathbf{v}}, \mathbf{i}, I_\mathbf{e} + 1)\end{array} & \text{if} \quad \hyperlink{I v}{I_\mathbf{v}} \leqslant \boldsymbol{\sigma}[I_\mathbf{a}]_\mathbf{b} \;\wedge\; I_\mathbf{e} < 1024 \\ (\boldsymbol{\sigma}, g, \varnothing, ()) & \text{otherwise} \end{cases}$ \\
&&&& Note the changes (in addition to that of the fourth parameter) to the second and ninth parameters to the call $\Theta$. This means that the recipient is in fact the same account as at present, simply that the code is overwritten {\it and} the context is almost entirely identical.\\
\midrule
0xfe & {\small INVALID} & $\varnothing$ & $\varnothing$ & Designated invalid instruction. \hypertarget{\mathrm{selfdestruct}}{}\\
\midrule
0xff & {\small SELFDESTRUCT} & 1 & 0 & Halt execution and register account for later deletion. \\
&&&& $A'_\mathbf{s} \equiv A_\mathbf{s} \cup \{ I_\mathbf{a} \}$ \\
&&&& $\boldsymbol{\sigma}'[\boldsymbol{\mu}_\mathbf{s}[0] \mod 2^{160}]_\mathbf{b} \equiv \boldsymbol{\sigma}[\boldsymbol{\mu}_\mathbf{s}[0] \mod 2^{160}]_\mathbf{b} + \boldsymbol{\sigma}[I_\mathbf{a}]_\mathbf{b}$ \\
&&&& $\boldsymbol{\sigma}'[I_\mathbf{a}]_\mathbf{b} \equiv 0$ \\
&&&& $A'_{r} \equiv A_{r} + \begin{cases}
\hyperlink{Rselfdestruct}{R_{\mathrm{selfdestruct}}} & \text{if} \quad I_\mathbf{a} \notin A_\mathbf{s} \\
0 & \text{otherwise} 
\end{cases}$ \hypertarget{C tiny SELFDESTRUCT}{}\\
&&&& $ C_{\text{\tiny SELFDESTRUCT}}(\boldsymbol{\sigma}, \boldsymbol{\mu}) \equiv \hyperlink{Gselfdestruct}{G_{\mathrm{selfdestruct}}} + \begin{cases}
\hyperlink{Gnewaccount}{G_{\mathrm{newaccount}}} & \text{if} \quad \boldsymbol{\sigma}[\boldsymbol{\mu}_\mathbf{s}[0] \mod 2^{160}] = \varnothing \\
0 & \text{otherwise}
\end{cases}$ \\
\bottomrule
\end{tabularx}

@@

\begin{tabularx}{\textwidth}{lrX}
%\begin{tabu}{X[,l]X[,r]X[,l]} 
\toprule
Name & Value & Description \hypertarget{Jwordbytes}{ \\
\midrule 
$J_{\mathrm{wordbytes}}$ & 4  & This is the bytes in a word. }\hypertarget{Jdatasetinit}{ \\
$J_{\mathrm{datasetinit}}$ & $2^{30}$ & This is the bytes in the dataset at genesis. }\hypertarget{Jdatasetgrowth}{ \\
$J_{\mathrm{datasetgrowth}}$ & $2^{23}$ & This is the dataset growth per epoch. }\hypertarget{Jcacheinit}{\\
$J_{\mathrm{cacheinit}}$ & $2^{24}$ & This is the bytes in the cache at genesis.}\hypertarget{Jcachegrowth}{\\
$J_{\mathrm{cachegrowth}}$ & $2^{17}$ & This is the cache growth per epoch.}\hypertarget{Jepoch}{\\
$J_{\mathrm{epoch}}$ & 30000 & This is the blocks per epoch.}\hypertarget{Jmixbytes}{\\
$J_{\mathrm{mixbytes}}$ & 128 & This is the mix length in bytes.}\hypertarget{Jhashbytes}{\\
$J_{\mathrm{hashbytes}}$ & 64 & This is the hash length in bytes.}\hypertarget{Jparents}{\\
$J_{\mathrm{parents}}$ & 256 & This is the number of parents of each dataset element.}\hypertarget{Jcacherounds}{\\
$J_{\mathrm{cacherounds}}$ & 3 & This is the number of rounds in cache production.}\hypertarget{Jaccesses}{\\
$J_{\mathrm{accesses}}$ & 64 & This is the number of accesses in a hashimoto loop.}\\
\bottomrule
%\end{tabu}
\end{tabularx}

>>>>

\documentclass[9pt,oneside]{amsart}
\usepackage{cancel}
%\usepackage{tweaklist}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{C3}{\"{e}}
\DeclareUnicodeCharacter{AD}{\Huge [ICI]}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{underscore}
%\usepackage{lipsum} % to generate filler text for testing of document rendering
\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\MakeOuterQuote{"}
\usepackage[bookmarks=true, unicode=true, pdftitle={Ethereum Yellow Paper: a formal specification of Ethereum, a programmable blockchain}, pdfauthor={Gavin Wood and others as per https://github.com/ethereum/yellowpaper/commits/master},pdfkeywords={Ethereum, Yellow Paper, blockchain, virtual machine, cryptography, decentralised, singleton, transaction, generalised},pdfborder={0 0 0.5 [1 3]}]{hyperref}
%,pagebackref=true

@@

% Tabu seems more flexible, and generally better.
\usepackage{tabu} %requires array.

@@

@@

$G_{\mathrm{memory}}$ & 3 & This is paid for every additional word when expanding memory. \hypertarget{Gtxcreate}{\\

@@

\begin{tabularx}{\textwidth}{rlrrX}
\midrule
0xf4 & {\small DELEGATECALL} & 6 & 1 & Message-call into this account with an alternative account's code, but persisting the current values for {\it sender} and {\it value}. Compared with {\small CALL}, {\small DELEGATECALL} takes one fewer arguments.  The omitted argument is $\boldsymbol{\mu}_\mathbf{s}[2]$. As a result, $\boldsymbol{\mu}_\mathbf{s}[3]$, $\boldsymbol{\mu}_\mathbf{s}[4]$, $\boldsymbol{\mu}_\mathbf{s}[5]$ and $\boldsymbol{\mu}_\mathbf{s}[6]$ in the definition of {\small CALL} should respectively be replaced with $\boldsymbol{\mu}_\mathbf{s}[2]$, $\boldsymbol{\mu}_\mathbf{s}[3]$, $\boldsymbol{\mu}_\mathbf{s}[4]$ and $\boldsymbol{\mu}_\mathbf{s}[5]$. Otherwise it is exactly equivalent to {\small CALL} except: \\
&&&& $(\boldsymbol{\sigma}', g', A^+, \mathbf{o}) \equiv \begin{cases}\begin{array}{l}\Theta(\boldsymbol{\sigma}^*, I_\mathbf{s}, I_\mathbf{o}, I_\mathbf{a}, t,\\\quad \boldsymbol{\mu}_\mathbf{s}[0], I_\mathbf{p}, 0, \hyperlink{I v}{I_\mathbf{v}}, \mathbf{i}, I_\mathbf{e} + 1)\end{array} & \text{if} \quad \hyperlink{I v}{I_\mathbf{v}} \leqslant \boldsymbol{\sigma}[I_\mathbf{a}]_\mathbf{b} \;\wedge\; I_\mathbf{e} < 1024 \\ (\boldsymbol{\sigma}, g, \varnothing, ()) & \text{otherwise} \end{cases}$ \\
&&&& Note the changes (in addition to that of the fourth parameter) to the second and ninth parameters to the call $\Theta$. This means that the recipient is in fact the same account as at present, simply that the code is overwritten {\it and} the context is almost entirely identical.\\
\midrule
0xfe & {\small INVALID} & $\varnothing$ & $\varnothing$ & Designated invalid instruction. \hypertarget{selfdestruct}{\\
\midrule
0xff & {\small SELFDESTRUCT} & 1 & 0 & Halt execution and register account for later deletion. }\\
&&&& $A'_\mathbf{s} \equiv A_\mathbf{s} \cup \{ I_\mathbf{a} \}$ \\
&&&& $\boldsymbol{\sigma}'[\boldsymbol{\mu}_\mathbf{s}[0] \mod 2^{160}]_\mathbf{b} \equiv \boldsymbol{\sigma}[\boldsymbol{\mu}_\mathbf{s}[0] \mod 2^{160}]_\mathbf{b} + \boldsymbol{\sigma}[I_\mathbf{a}]_\mathbf{b}$ \\
&&&& $\boldsymbol{\sigma}'[I_\mathbf{a}]_\mathbf{b} \equiv 0$ \\
&&&& $A'_{r} \equiv A_{r} + \begin{cases}
\hyperlink{Rselfdestruct}{R_{\mathrm{selfdestruct}}} & \text{if} \quad I_\mathbf{a} \notin A_\mathbf{s} \\
0 & \text{otherwise} 
\end{cases}$ \hypertarget{C tiny SELFDESTRUCT}{}\\
&&&& $ C_{\text{\tiny SELFDESTRUCT}}(\boldsymbol{\sigma}, \boldsymbol{\mu}) \equiv \hyperlink{Gselfdestruct}{G_{\mathrm{selfdestruct}}} + \begin{cases}
\hyperlink{Gnewaccount}{G_{\mathrm{newaccount}}} & \text{if} \quad \boldsymbol{\sigma}[\boldsymbol{\mu}_\mathbf{s}[0] \mod 2^{160}] = \varnothing \\
0 & \text{otherwise}
\end{cases}$ \\
\bottomrule
\end{tabularx}

@@

%\begin{tabularx}{\textwidth}{lrX}
\begin{tabu}{X[,l]X[,r]X[,l]} 
\toprule
Name & Value & Description \hypertarget{Jwordbytes}{\\
\midrule 
$J_{\mathrm{wordbytes}}$ & 4  & This is the bytes in a word.}\hypertarget{Jdatasetinit}{\\
$J_{\mathrm{datasetinit}}$ & $2^{30}$ & This is the bytes in the dataset at genesis. }\hypertarget{Jdatasetgrowth}{\\
$J_{\mathrm{datasetgrowth}}$ & $2^{23}$ & This is the dataset growth per epoch. }\hypertarget{Jcacheinit}{\\
$J_{\mathrm{cacheinit}}$ & $2^{24}$ & This is the bytes in the cache at genesis.}\hypertarget{Jcachegrowth}{\\
$J_{\mathrm{cachegrowth}}$ & $2^{17}$ & This is the cache growth per epoch.}\hypertarget{Jepoch}{\\
$J_{\mathrm{epoch}}$ & 30000 & This is the blocks per epoch.}\hypertarget{Jmixbytes}{\\
$J_{\mathrm{mixbytes}}$ & 128 & This is the mix length in bytes.}\hypertarget{Jhashbytes}{\\
$J_{\mathrm{hashbytes}}$ & 64 & This is the hash length in bytes.}\hypertarget{Jparents}{\\
$J_{\mathrm{parents}}$ & 256 & This is the number of parents of each dataset element.}\hypertarget{Jcacherounds}{\\
$J_{\mathrm{cacherounds}}$ & 3 & This is the number of rounds in cache production.}\hypertarget{Jaccesses}{\\
$J_{\mathrm{accesses}}$ & 64 & This is the number of accesses in a hashimoto loop.}\\
\bottomrule
\end{tabu}
%\end{tabularx}
